working title Compatibility system and stigma size are the main predictors of heterospecific pollen effect

### 2019-02-26 Manuscript_draft/Manuscript_draft.Rmd
Some edits to be able to knit on mac

The traits measured for each species were pollen per anther, number of ovules and stigma, style, ovary width and length. For the stigma, the stigmatic area was also measured and moreover the stigmas were divided in wet/dry type. All the morphometrical measurements were performed with a stereophotomicroscope. Pollen was counted for 20 anthers of each species with 4 replicates per sample with an hemocytometer. Previously, anthers were squashed on a known solution with the pippete tip and homogeneize with a vortex for 30 seconds. Ovule number was counted with the help of an stereomicroscope and a small grid over a petri dish from 15 randomly selected flowers. Fruits per number of flowers treated were counted for Solanaceae species and for the rest, the number of seeds produced per average number of ovules of each species. Levels of self incompatibility were estimated by dividing the fruit set of hand self pollination by hand cross pollination @lloyd1992.

@@

Results of hand cross-pollination, self hand-pollination, natural selfing and apomixis are presented in **Figure 1** (see appendix 1 for values). Heterospecific pollen reduced seet set signifcatively with the 50-50% heterospecific pollen treatments for 65% of the pairwise interactions p<0.05.

@@

ggplot(bio,aes(x=Species,y=value,fill=variable))+
  geom_bar(stat="identity",position="dodge")+scale_fill_grey(start = 0, end = 0.85,name="Treatments") + 
  theme_minimal()+xlab("Species")+ylab("Seed-setting rate (%)")+labs(title="Reproductive biology tests")+
  theme(axis.text.x = element_text(angle = 35, hjust = 1, face= "italic",family = "Arial Narrow"), legend.text=element_text(size=7), legend.title=element_text(size=8), axis.text.y  = element_text(size = 10))+
  scale_y_continuous(minor_breaks = seq(0 , 100, 5), breaks = seq(0, 100, 10))

>>>>

The traits measured for each species were pollen per anther, number of ovules and stigma, style, ovary width and length. For the stigma, the stigmatic area was also measured and moreover the stigmas were divided in wet/dry type. All the morphometrical measurements were performed with a stereophotomicroscope. Pollen was counted for 20 anthers of each species with 4 replicates per sample with an hemocytometer. Previously, anthers were squashed on a known solution with the pippete tip and homogeneize with a vortex for 30 seconds. Ovule number was counted with the help of a stereomicroscope and a small grid over a petri dish from 15 randomly selected flowers. Fruits per number of flowers treated were counted for Solanaceae species and for the rest, the number of seeds produced per average number of ovules of each species. Levels of self incompatibility were estimated by dividing the fruit set of hand self pollination by hand cross pollination @lloyd1992.

@@

Results of hand cross-pollination, self hand-pollination, natural selfing and apomixis are presented in **Figure 1** (see appendix 1 for table with values). Heterospecific pollen reduced seet set significatively with the 50-50% heterospecific pollen treatments for 65% of the pairwise interactions p<0.05.

@@

ggplot(bio,aes(x=Species,y=value,fill=variable))+
  geom_bar(stat="identity",position="dodge")+scale_fill_grey(start = 0, end = 0.85,name="Treatments") + 
  theme_minimal()+xlab("Species")+ylab("Seed-setting rate (%)")+labs(title="Reproductive biology tests")+
  theme(axis.text.x = element_text(angle = 35, hjust = 1, face= "italic",family = ""), legend.text=element_text(size=7), legend.title=element_text(size=8), axis.text.y  = element_text(size = 10))+
  scale_y_continuous(minor_breaks = seq(0 , 100, 5), breaks = seq(0, 100, 10))

### 2019-02-26 Manuscript_draft/Manuscript_draft.tex
changes
Some edits to be able to knit on mac

The traits measured for each species were pollen per anther, number of
ovules and stigma, style, ovary width and length. For the stigma, the
stigmatic area was also measured and moreover the stigmas were divided
in wet/dry type. All the morphometrical measurements were performed with
a stereophotomicroscope. Pollen was counted for 20 anthers of each
species with 4 replicates per sample with an hemocytometer. Previously,
anthers were squashed on a known solution with the pippete tip and
homogeneize with a vortex for 30 seconds. Ovule number was counted with
the help of an stereomicroscope and a small grid over a petri dish from
15 randomly selected flowers. Fruits per number of flowers treated were
counted for Solanaceae species and for the rest, the number of seeds
produced per average number of ovules of each species. Levels of self
incompatibility were estimated by dividing the fruit set of hand self
pollination by hand cross pollination Lloyd and Schoen (1992).

@@

Results of hand cross-pollination, self hand-pollination, natural
selfing and apomixis are presented in \textbf{Table 2}. Heterospecific
pollen reduced seet set signifcatively with the 50-50\% heterospecific
pollen treatments for 65\% of the pairwise interactions
p\textless{}0.05.

@@

\textbf{Table 2}. Perecentage of seeds produced per ovule for the ten
species used in the experiment. The treatments presented are hand cross
pollination, hand self pollination, natural selfing and apomixis
(emasculated flowers). \href{}{turn into a figure somehow?}

\begin{figure}
\centering
\includegraphics{output/figures/unnamed-chunk-3-1.pdf}
\caption{Barplot with the different treatments that provide information
of the reproductive biology of the ten species. The y axis is the
proportion of ovules converted to seed in percentage. The different
treatments (N=10) which are presented in the legend are, hand cross
pollination, hand self pollination, natural selfing and apomixis. More
information about these treatments can be found in Methods and
Appendices.}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics{output/figures/unnamed-chunk-4-1.pdf}
\caption{The effect of heterospecific pollen (scaled see set) is
represented in function of the compatibility system (self/cross*100) for
the the different species. Each coulored dot represents the interaction
of a focal species with a different pollen donor.}
\end{figure}

@@

>>>>

The traits measured for each species were pollen per anther, number of
ovules and stigma, style, ovary width and length. For the stigma, the
stigmatic area was also measured and moreover the stigmas were divided
in wet/dry type. All the morphometrical measurements were performed with
a stereophotomicroscope. Pollen was counted for 20 anthers of each
species with 4 replicates per sample with an hemocytometer. Previously,
anthers were squashed on a known solution with the pippete tip and
homogeneize with a vortex for 30 seconds. Ovule number was counted with
the help of a stereomicroscope and a small grid over a petri dish from
15 randomly selected flowers. Fruits per number of flowers treated were
counted for Solanaceae species and for the rest, the number of seeds
produced per average number of ovules of each species. Levels of self
incompatibility were estimated by dividing the fruit set of hand self
pollination by hand cross pollination Lloyd and Schoen (1992).

@@

Results of hand cross-pollination, self hand-pollination, natural
selfing and apomixis are presented in \textbf{Figure 1} (see appendix 1
for table with values). Heterospecific pollen reduced seet set
significatively with the 50-50\% heterospecific pollen treatments for
65\% of the pairwise interactions p\textless{}0.05.

@@

\begin{figure}
\centering
\includegraphics{output/figures/unnamed-chunk-2-1.pdf}
\caption{Barplot with the different treatments that provide information
of the reproductive biology of the ten species. The y axis is the
proportion of ovules converted to seed in percentage. The different
treatments (N=10) which are presented in the legend are, hand cross
pollination, hand self pollination, natural selfing and apomixis. More
information about these treatments can be found in Methods and
Appendices.}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics{output/figures/unnamed-chunk-3-1.pdf}
\caption{The effect of heterospecific pollen (scaled see set) is
represented in function of the compatibility system (self/cross*100) for
the the different species. Each coulored dot represents the interaction
of a focal species with a different pollen donor.}
\end{figure}

@@

\section{APPENDIX}\label{appendix}

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\item
\end{enumerate}

\textbf{Table S1}. Perecentage of seeds produced per ovule for the ten
species used in the experiment. The treatments presented are hand cross
pollination, hand self pollination, natural selfing and apomixis
(emasculated flowers).
